---
title: "SuperCENT Simulation"
author: "Junhui Cai, Dan Yang, Wu Zhu, Haipeng Shen, Linda Zhao"
output: 
  pdf_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(data.table, matrixStats, dplyr, ggplot2, ggpubr,
               grid, gridExtra, gtable, latex2exp, facetscales)

source("utils_sim.R")

sim_setup <- NULL
fig_width <- 12
fig_height <- 6

knitr::opts_chunk$set(echo = F, fig.height = fig_height, fig.width = fig_width)
```

This file is produced by `SuperCENT_simulation.Rmd` which contains both codes to reproduce the simulation results in "Network Regression and Supervised Centrality Estimation" and the descriptions and instructions of the code chunks.
To reproduce this report, `Knit` this file in RStudio.
One can set `echo = T` for the each chunk or globally `knitr::opts_chunk$set(echo = T)` to show the code in the report.


# Simulation

The simulations were run on the Sun Grid Engine (SGE) on Red Hat Enterprise Linux. 
The main run file is `confint.R` with utility functions in `utils_sim.R`. 
The setup of parameters $n, d, \beta_u, \beta_v, \beta_x$ therein is set using the `optparse` package
and is specified in `option_list` with descriptions for each options.

To run different settings on SGE, specify the parameters grid in `run_confint.sh` and run `qsub run_confint.sh` in the `code` folder.
It will write a summary log in `../output/<job-name>_<job-id>.log` and submit multiple jobs each with different setting with the results saved in `../hpcc_output/confint_<job-id>`.
To combine the simulation results, run `Rscript reduce_cv.R <job-id>` where `job-id` is the job-id of the SGE. 
If one does not use SGE, run `Rscript confint.R --help` to print out a brief summary of the options and specify the settings accordingly. For example, `Rscript confint.R --betau 4` to set $\beta_u = 2^4$.


# Toy experiment

```{r}
params <- NULL
params$job_id <- c(1745349)
params$job_name <- "confint"

sim_setup <- read_setup(params = params)
ret <- read_output(params = params)

ret <- ret[log2(epsa) >= 1]
epsa_sel <- seq(1, 5, .5)
sim_setup$epsas <- sim_setup$epsas[sim_setup$epsas %in% epsa_sel]

betavv <- 1

fig_width <- 8
fig_height <- 12
```

## Figure 1

The following chunk produces the toy experiment in the introduction.

```{r}
epsyy <- -2

methods <- c("ols", "lr_oracle")

ret[, sinu := sqrt(u^2)  ] 
p1 <- plot_line_mean(ret[betav == 1 & betau == 16 & log2(epsy) == epsyy], 
               methods, value = "sinu",
               FUN = mean,
               scale_y_transform = identity,
               xaxis = "epsa",
               hpanel = "epsy",
               save = save, width = fig_width, height = fig_height,
               # subtitle = TeX("$\\sin(angle(\\widehat{u}, u))$"),
               title = TeX("Estimation error of hub centrality $u$"),
               x_breaks = epsa_sel, 
               x_lab_pre = "Network noise: "
               # value0 = "u_0", 
               # gray = F
)


ret[, bias_betau := (hbetau - betau)]
p2 <- plot_line_mean(ret[betav == 1 & betau == 16 & log2(epsy) == epsyy], methods, 
               value = "bias_betau",
               FUN = mean,
               scale_y_transform = identity,
               xaxis = "epsa",
               hpanel = "epsy",
               save = save, width = fig_width, height = fig_height,
               x_breaks = epsa_sel, 
               title = TeX("Estimation bias of hub effect $\\beta_u$"), 
               # subtitle = TeX("$\\widehat{\\beta}_u - \\beta_u$"),
               x_lab_pre = "Network noise: "
               # value0 = "u_0", 
               # gray = F
)

methods <- c("ols", "lr_oracle_oracle")
p3 <- plot_line_mean(ret[betav == betavv & betau == 16 & log2(epsy) == epsyy], methods, 
               value = "cov_u",
               FUN = mean,
               error_bar = F, 
               scale_y_transform = I,
               xaxis = "epsa",
               hpanel = "epsy",
               save = save,
               x_breaks = epsa_sel, 
               # title = TeX("Coverage of $CI_{\\beta_u}$") ,
               # title = TeX("Empirical coverage of  $CI_{\\beta_u}$") ,
               title = TeX("Coverage probablity of $CI_{\\beta_u}$"), 
               x_lab_pre = "Network noise: ",
               width = fig_width, height = fig_height)

p4 <- plot_line_mean(ret[betav == betavv & betau == 16 & log2(epsy) == epsyy], methods, 
               value = "width_u",
               FUN = median,
               error_bar = F, 
               scale_y_transform = I,
               xaxis = "epsa",
               hpanel = "epsy",
               save = save,
               x_breaks = epsa_sel, 
               title = TeX("Width of $CI_{\\beta_u}$") , 
               x_lab_pre = "Network noise: ",
               width = fig_width, height = fig_height)

prow <- cowplot::plot_grid( p1 + theme(legend.position="none"),
           p2 + theme(legend.position="none"),
           p3 + theme(legend.position="none"),
           p4 + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B", "C", "D"),
           hjust = -4,
           nrow = 2
           )
prow
# extract the legend from one of the plots
# (clearly the whole thing only makes sense if all plots
# have the same legend, so we can arbitrarily pick one.)
legend_b <- cowplot::get_legend(
  p1 + 
    guides(color = guide_legend(nrow = 1))+ 
    theme(legend.position="bottom")
)


# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- cowplot::plot_grid( prow, legend_b, ncol = 1, rel_heights = c(1, .1))
p

ggsave(paste0("../output_simulation/plot/",
              paste(sim_setup$job_id, collapse = "-"), "_epsy",
              epsyy,
              "_small_exmaple.pdf"), 
       width = 12, height = 8)
```


# Consistent regime of two-stage

This section is for the plots of the consistent regime of the two-stage procedure.

```{r}
params <- NULL
params$job_id <- 1740961 # epsa/epsy: -6 -5 -4 -3 -2 -1 0; betau: 0, 2, 4; betav: 0; xmat: c; n: 8
params$job_name <- "confint"

sim_setup <- read_setup(params = params)
ret <- read_output(params = params)

epsy_sel <- c(-4, -2, 0)
epsa_sel <- c(-4, -2)
ret <- ret[log2(epsy) %in% epsy_sel & log2(epsa) %in% epsa_sel]
sim_setup$epsys <- sim_setup$epsys[sim_setup$epsys %in% epsy_sel]
sim_setup$epsas <- sim_setup$epsas[sim_setup$epsas %in% epsa_sel]

save <- T

betavv <- 1

fig_width <- 12
fig_height <- 6
```

## Calculation of theoretical results

We first calculate the theoretical rate of $\hat{u}$, $\hat{v}$ and $\hat{A}$ as well as $\hat{\beta}_u$ and $\hat{\beta}_v$.

```{r include=FALSE}
theorectical_property(params = params)
theo <- read_theorectical(params = params)
theo <- unique(theo)
setnames(theo, c("method", "lopt"), 
         c("method_class", "lopt0"))
theo[,beta0:=NULL]
ret[, method_class := "two_stage"]
ret[grepl("lr", method), method_class := "supercent"]
ret <- merge(ret, theo,
             by = c("method_class", "epsy", "epsa", "n", "betau", "betav", "d"),
             all.x = T)
```


```{r}
n <- 2^sim_setup$ns

# u, v
ret[, u := u^2]
ret[, u_f := u_f/n]
ret[, v := v^2]
ret[, v_f := v_f/n]

if("A2" %in% names(ret)) {
  ret[, A_norm := A_err/A2]
}
if("A0_2" %in% names(ret)) {
  ret[, A_norm := A_err/A0_2]
}

# beta
ret[, rate_betau := (betau - betau_hat)^2/betau^2]
ret[, rate_betav := (betav - betav_hat)^2/betav^2]
```

## Estimation property

For the estimation accuracy, we compare the following procedures:
\begin{enumerate}
	\item \textbf{Two-stage}: the two-stage procedure as in Algorithm1;
	\item \textbf{SuperCENT-$\lambda_0$}: SuperCENT Algorithm 2 with the optimal $\lambda_0 = n\sigma_y^2/\sigma_a^2$, where the true $\sigma_y,\sigma_a$ are used;
	\item \textbf{SuperCENT-$\hat\lambda_0$}: SuperCENT with estimated tuning parameter $\hat\lambda_0 = n(\hat\sigma_y^{ts})^2/(\hat\sigma_a^{ts})^2$, where $(\hat\sigma_y^{ts})^2 = \frac{1}{n-p-2}\|\hat{y}^{ts}-y\|_2^2$ and $(\hat\sigma_a^{ts})^2 = \frac{1}{n^2} \|\hat{A}^{ts} - A_0\|_F^2$ are estimated from the two-stage procedure;
	\item \textbf{SuperCENT-$\hat\lambda_{cv}$}: SuperCENT with tuning parameter $\hat\lambda_{cv}$ chosen by 10-fold {cross-validation}.
\end{enumerate}

```{r}
methods <- c("two_stage", # two-stage
             "lr_oracle", # SuperCENT-$\lambda_0$
             "lr_plugin", # SuperCENT-$\hat\lambda_0$
             "lr_cv"  # SuperCENT-$\hat\lambda_{cv}$
)
```

### u and v

The following chunks produce the plots of $l(\widehat{u}, u)$ and $l(\widehat{v}, v)$.

```{r}
plot_boxplot(ret[betav == betavv], methods, value = "u",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l(\\widehat{u}, u)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "u_0", 
             gray = F
             )
```

```{r}
plot_boxplot(ret[betav == betavv], methods, value = "v",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l(\\widehat{v}, v)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "v_0", 
             gray = F
             )
```

### A 

The following chunk produces the plot of $l(\widehat{A}, A_0)$.

```{r}
ret[, A_norm := A_err/A0_2]
plot_boxplot(ret[betav == betavv], methods, value = "A_norm",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$ l (\\widehat{A}, A_0)$"), 
             save = T, width = fig_width, height = fig_height,
             value0 = "A_norm_0", 
             gray = F
             )
```


### $\beta_u$ and  $\beta_v$

The following chunks produce the plots of $l (\widehat{\beta}_u, \beta_u)$ and $l (\widehat{\beta}_v, \beta_v)$.

```{r}
ret[, rate_betau := (betau - hbetau)^2/betau^2]
scales_y <- list(
  `-4` = scale_y_continuous(limits = c(-10, -1)),
  `-2` = scale_y_continuous(limits = c(-9, -1)))

plot_boxplot(ret[betav == betavv], methods, value = "rate_betau",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l (\\widehat{\\beta}_u, \\beta_u)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "betau_0", 
             y_scales = scales_y,
             gray = F)
```

```{r}
ret[, rate_betav := (betav - hbetav)^2/betav^2]
plot_boxplot(ret[betav == betavv], methods, value = "rate_betav",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l (\\widehat{\\beta}_v, \\beta_v)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "betav_0", 
             y_scales = scales_y,
             gray = F)
```

The following chunks produce the plots of $\widehat{\beta}_u -\beta_u$ and $\widehat{\beta}_v - \beta_v$.

```{r}
param_groups <- c("method", "epsy", "epsa", "betau", "betav", "d")
ret[, bias_betau := (hbetau - betau)]
ret[, bias_betau_median := median(bias_betau), by = param_groups]

plot_boxplot(ret[betav == betavv], methods, value = "bias_betau",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             scale_y_transform = identity,
             title = TeX("$\\widehat{\\beta}_u - \\beta_u$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "bias_betau_median",
             ylim = c(-.1,.1),
             gray = F)
```


```{r}
ret[, bias_betav := (hbetav - betav)]
ret[, bias_betav_median := median(bias_betav), by = param_groups]

plot_boxplot(ret[betav == betavv], methods, value = "bias_betav",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             scale_y_transform = identity,
             title = TeX("$\\widehat{\\beta}_v - \\beta_v$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "bias_betav_median",
             ylim = c(-.1,.1),
             gray = F)
```

## Inference property

For the inference property, let $z_{1-\alpha/2}$ denote the $(1-\alpha/2)$-quantile of the standard normal distribution and we consider the following procedures to construct the confidence intervals (CIs) for the regression coefficient,
{$CI_{\beta_u}$ and $CI_{\beta_v}$:}
\begin{enumerate}
	\item \textbf{Two-stage-{adhoc}}: 
	$\hat\beta^{ts} \pm z_{1-\alpha/2} \hat\sigma^{OLS}(\hat\beta^{ts})$, where $\hat\beta^{ts}$ is the two-stage estimate of $\beta$ and $\hat\sigma^{OLS}(\hat\beta^{ts})$ is the standard error from OLS,  assuming $\hat{u}^{ts},\hat{v}^{ts}$ are fixed predictors;
	\item \textbf{Two-stage-oracle}: 
	$\hat\beta^{ts}  \pm z_{1-\alpha/2} \sigma(\hat\beta^{ts})$, where $\sigma(\hat\beta^{ts})$ is the standard error of $\hat\beta^{ts}$, whose mathematical expressions are given in Corollary 2 and the true parameters are plugged into those expressions;
	\item \textbf{Two-stage}: 
	$\hat\beta^{ts} \pm z_{1-\alpha/2} \hat\sigma(\hat\beta^{ts})$, where $\hat\sigma(\hat\beta^{ts})$ is the standard error of $\hat\beta^{ts}$ by plugging all the two-stage estimators into Corollary 2.
	\item \textbf{SuperCENT-$\lambda_{0}$-oracle};
	$\hat\beta^{\lambda_0} \pm z_{1-\alpha/2}  \sigma(\hat\beta^{\lambda_0})$, where $\hat\beta^{\lambda_0}$ is the estimate of $\beta$ by SuperCENT-$\lambda_{0}$ and $\sigma(\hat\beta^{\lambda_0})$ follows Corollary 5, with the true parameters plugged in;
	\item \textbf{SuperCENT-$\hat\lambda_{cv}$}:
	 $\hat\beta^{\hat{\lambda}_{cv}} \pm z_{1-\alpha/2} \hat\sigma(\hat\beta^{\hat{\lambda}_{cv}})$, where $\hat\beta^{\hat{\lambda}_{cv}}$ is the estimate of $\beta$ by SuperCENT-$\hat\lambda_{cv}$ and $\hat\sigma(\hat\beta^{\hat{\lambda}_{cv}})$ is obtained by plugging the SuperCENT-$\hat\lambda_{cv}$ estimates into Corollary 5.
\end{enumerate}

```{r}
methods <- c("ols", # Two-stage-{adhoc}
             "two_stage_oracle", # Two-stage-oracle
             "two_stage", # Two-stage
             "lr_oracle_oracle",  # SuperCENT-$\lambda_{0}$-oracle
             "lr_cv" # SuperCENT-$\hat\lambda_{cv}$
             )
```

### Coverage of $CI_{\beta_u}$ and  $CI_{\beta_v}$

The following chunks produce the plots of the empirical coverage of the 95\% confidence interval for $\beta_u$ and $\beta_v$ respectively, i.e., $CP(CI_{\beta_u})$ and  $CP(CI_{\beta_v})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_u",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("$CP(CI_{\\beta_u})$"),
          # ylim = (.9,1),
          width = fig_width, height = fig_height)
```

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_v",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("$CP(CI_{\\beta_v})$"),
          width = fig_width, height = fig_height)
```


### Width of $CI_{\beta_u}$ and  $CI_{\beta_v}$

The following chunks produce the plots of the average of width of the 95\% confidence interval for $\beta_u$ and $\beta_v$ respectively, i.e., $Width(CI_{\beta_u})$ and  $Width(CI_{\beta_v})$.


```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_u",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Width($CI_{\\beta_u})$") ,
          width = fig_width, height = fig_height)
```


```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_v",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Width($CI_{\\beta_v})$") ,
          width = fig_width, height = fig_height)
```


### Coverage of $CI_{a_{ij}}$

```{r}
methods <- c("two_stage_oracle", # Two-stage-oracle
             "two_stage", # Two-stage
             "lr_oracle_oracle",  # SuperCENT-$\lambda_{0}$-oracle
             "lr_cv" # SuperCENT-$\hat\lambda_{cv}$
             )
```

The following chunk produces the plots of the average empirical coverage of the 95\% confidence interval for each entry of $A_0$, i.e., $CP(CI_{a_{ij}})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_A",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Average_{ij}($CP(CI_{a_{ij}}))$") ,
          width = fig_width, height = fig_height,
          ylim = c(.9, 1),
          scales = "free")
```


### Width of $CI_{a_{ij}}$

The following chunk produces the plots of the average width of the 95\% confidence interval for each entry of $A_0$, i.e., $Width(CI_{a_{ij}})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_A",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Average_{ij}($Width(CI_{a_{ij}}))$") ,
          width = fig_width, height = fig_height)
```


# Inconsistent regime of two-stage

This section is for the plots of the inconsistent regime of the two-stage procedure.

```{r}
params <- NULL
params$job_id <- c(1741112, 1740961) # epsa: 1 2 3 4; epsy: -6 -5 -4 -3 -2 -1 0; betau: 0, 2, 4; betav: 0; xmat: c; n: 8
params$job_name <- "confint"

sim_setup <- read_setup(params = params)
ret <- read_output(params = params)

epsy_sel <- c(-4, -2, 0)
epsa_sel <- c(0, 2)
ret <- ret[log2(epsy) %in% epsy_sel & log2(epsa) %in% epsa_sel]
sim_setup$epsys <- sim_setup$epsys[sim_setup$epsys %in% epsy_sel]
sim_setup$epsas <- sim_setup$epsas[sim_setup$epsas %in% epsa_sel]

betavv= 1
save <- T

fig_width <- 12
fig_height <- 6
```


## Calculation of theoretical results

```{r include=FALSE}
theorectical_property(params = params)
theo <- read_theorectical(params = params)
theo <- unique(theo)
setnames(theo, c("method", "lopt"), 
         c("method_class", "lopt0"))
theo[,beta0:=NULL]
ret[, method_class := "two_stage"]
ret[grepl("lr", method), method_class := "supercent"]
ret <- merge(ret, theo,
             by = c("method_class", "epsy", "epsa", "n", "betau", "betav", "d"),
             all.x = T)
```


```{r}
n <- 2^sim_setup$ns

# u, v
ret[, u := u^2]
ret[, u_f := u_f/n]
ret[, v := v^2]
ret[, v_f := v_f/n]

if("A2" %in% names(ret)) {
  ret[, A_norm := A_err/A2]
}
if("A0_2" %in% names(ret)) {
  ret[, A_norm := A_err/A0_2]
}

# beta
ret[, rate_betau := (betau - betau_hat)^2/betau^2]
ret[, rate_betav := (betav - betav_hat)^2/betav^2]
```

## Estimation property

For the estimation accuracy, we compare the following procedures:
\begin{enumerate}
	\item \textbf{Two-stage}: the two-stage procedure as in Algorithm1;
	\item \textbf{SuperCENT-$\lambda_0$}: SuperCENT Algorithm 2 with the optimal $\lambda_0 = n\sigma_y^2/\sigma_a^2$, where the true $\sigma_y,\sigma_a$ are used;
	\item \textbf{SuperCENT-$\hat\lambda_0$}: SuperCENT with estimated tuning parameter $\hat\lambda_0 = n(\hat\sigma_y^{ts})^2/(\hat\sigma_a^{ts})^2$, where $(\hat\sigma_y^{ts})^2 = \frac{1}{n-p-2}\|\hat{y}^{ts}-y\|_2^2$ and $(\hat\sigma_a^{ts})^2 = \frac{1}{n^2} \|\hat{A}^{ts} - A_0\|_F^2$ are estimated from the two-stage procedure;
	\item \textbf{SuperCENT-$\hat\lambda_{cv}$}: SuperCENT with tuning parameter $\hat\lambda_{cv}$ chosen by 10-fold {cross-validation}.
\end{enumerate}

```{r}
methods <- c("two_stage", # two-stage
             "lr_oracle", # SuperCENT-$\lambda_0$
             "lr_plugin", # SuperCENT-$\hat\lambda_0$
             "lr_cv"  # SuperCENT-$\hat\lambda_{cv}$
)
```

### u and v

The following chunks produce the plots of $l(\widehat{u}, u)$ and $l(\widehat{v}, v)$.

```{r}
plot_boxplot(ret[betav == betavv], methods, value = "u",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l(\\widehat{u}, u)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "u_0", 
             gray = F
             )
```

```{r}
plot_boxplot(ret[betav == betavv], methods, value = "v",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l(\\widehat{v}, v)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "v_0", 
             gray = F
             )
```

### A 

The following chunk produces the plot of $l(\widehat{A}, A_0)$.

```{r}
ret[, A_norm := A_err/A0_2]
plot_boxplot(ret[betav == betavv], methods, value = "A_norm",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$ l (\\widehat{A}, A_0)$"), 
             save = T, width = fig_width, height = fig_height,
             value0 = "A_norm_0", 
             gray = F
             )
```


### $\beta_u$ and  $\beta_v$

The following chunks produce the plots of $l (\widehat{\beta}_u, \beta_u)$ and $l (\widehat{\beta}_v, \beta_v)$.

```{r}
param_groups <- c("method", "epsy", "epsa", "betau", "betav", "d")
ret[, rate_betau := (betau - hbetau)^2/betau^2]
ret[, rate_betau_median := median(rate_betau), by = param_groups]
scales_y <- list(
  `0` = scale_y_continuous(limits = c(-7, -1)),
  `2` = scale_y_continuous(limits = c(-5.5, -1.5))
)

plot_boxplot(ret[betav == betavv], methods, value = "rate_betau",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l (\\widehat{\\beta}_u, \\beta_u)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "rate_betau_median", 
             y_scales = scales_y,
             gray = F)
```

```{r}
ret[, rate_betav := (betav - hbetav)^2/betav^2]
ret[, rate_betav_median := median(rate_betav), by = param_groups]
scales_y <- list(
  `0` = scale_y_continuous(limits = c(-6, -1)),
  `2` = scale_y_continuous(limits = c(-5.5, 1))
)

plot_boxplot(ret[betav == betavv], methods, value = "rate_betav",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             title = TeX("$l (\\widehat{\\beta}_v, \\beta_v)$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "rate_betav_median", 
             y_scales = scales_y,
             gray = F)
```


The following chunks produce the plots of $\widehat{\beta}_u -\beta_u$ and $\widehat{\beta}_v - \beta_v$.

```{r}
param_groups <- c("method", "epsy", "epsa", "betau", "betav", "d")
ret[, bias_betau := (hbetau - betau)]
ret[, bias_betau_median := median(bias_betau), by = param_groups]

plot_boxplot(ret[betav == betavv], methods, value = "bias_betau",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             scale_y_transform = identity,
             title = TeX("$\\widehat{\\beta}_u - \\beta_u$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "bias_betau_median",
             # ylim = c(-.1,.1),
             gray = F)
```


```{r}
ret[, bias_betav := (hbetav - betav)]
ret[, bias_betav_median := median(bias_betav), by = param_groups]

plot_boxplot(ret[betav == betavv], methods, value = "bias_betav",
             FUN = median,
             vpanel = "betau",
             hpanel = "epsa",
             scale_y_transform = identity,
             title = TeX("$\\widehat{\\beta}_v - \\beta_v$"),
             save = T, width = fig_width, height = fig_height,
             value0 = "bias_betav_median",
             gray = F)
```


## Inference property

This subsection is for the
confidence intervals (CIs) for the regression coefficient,
{$CI_{\beta_u}$ and $CI_{\beta_v}$.


```{r}
methods <- c("ols", # Two-stage-{adhoc}
             "two_stage_oracle", # Two-stage-oracle
             "two_stage", # Two-stage
             "lr_oracle_oracle",  # SuperCENT-$\lambda_{0}$-oracle
             "lr_cv" # SuperCENT-$\hat\lambda_{cv}$
             )
```

### Coverage of $CI_{\beta_u}$ and  $CI_{\beta_v}$

The following chunks produce the plots of the empirical coverage of the 95\% confidence interval for $\beta_u$ and $\beta_v$ respectively, i.e., $CP(CI_{\beta_u})$ and  $CP(CI_{\beta_v})$.


```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_u",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("$CP(CI_{\\beta_u})$"),
          width = fig_width, height = fig_height)
```

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_v",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("$CP(CI_{\\beta_v})$"),
          width = fig_width, height = fig_height)
```



### Width of $CI_{\beta_u}$ and  $CI_{\beta_v}$

The following chunks produce the plots of the average of width of the 95\% confidence interval for $\beta_u$ and $\beta_v$ respectively, i.e., $Width(CI_{\beta_u})$ and  $Width(CI_{\beta_v})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_u",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Width($CI_{\\beta_u})$") ,
          width = fig_width, height = fig_height)
```


```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_v",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Width($CI_{\\beta_v}$)") ,
          width = fig_width, height = fig_height)
```


### Coverage of $CI_{a_{ij}}$

```{r}
methods <- c("two_stage_oracle", # Two-stage-oracle
             "two_stage", # Two-stage
             "lr_oracle_oracle",  # SuperCENT-$\lambda_{0}$-oracle
             "lr_cv" # SuperCENT-$\hat\lambda_{cv}$
             )
```

The following chunk produces the plots of the average empirical coverage of the 95\% confidence interval for each entry of $A_0$, i.e., $CP(CI_{a_{ij}})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "cov_A",
          FUN = mean,
          error_bar = F, 
          scale_y_transform = I,
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Average_{ij}($CP(CI_{a_{ij}}))$") ,
          width = fig_width, height = fig_height,
          scales = "fixed")
```

### Width of $CI_{a_{ij}}$

The following chunk produces the plots of the average width of the 95\% confidence interval for each entry of $A_0$, i.e., $Width(CI_{a_{ij}})$.

```{r}
plot_mean(ret[betav == betavv], methods, 
          value = "width_A",
          FUN = median,
          error_bar = F, 
          hpanel = "epsa",
          vpanel = "betau",
          save = save,
          title = TeX("Average_{ij}($Width(CI_{a_{ij}}))$") ,
          width = fig_width, height = fig_height)
```

